---
title: 'Beauty & Labor Market'
author: "Kenyon Williams"

date: "11/21/19"
output:
  html_document: default
  header-includes: \usepackage{color}
fontsize: 12pt
margin: 1in
---

```{r setup, echo=FALSE, message=F, warning=F}

#==============================================================================
#   This chunk will be used for every assignment
#==============================================================================

  # Clear the working space
    rm(list = ls())

  #Set working directory
setwd("/Users/kwill/Desktop/Econ 42")
#getwd()

### Load the packages (all must have been installed)
    library(doBy)
    library(dplyr)
    library(foreign)
    library(ggplot2)
    library(knitr)
    library(lmtest)
    library(readstata13)
    library(sandwich)
    library(stargazer)
    library(AER)
    library(gdata)

cse=function(reg) {
rob=sqrt(diag(vcovHC(reg, type="HC1")))
return(rob)
}

```
### INTERACTION TERMS

```{r data, echo=FALSE, warning=FALSE, include=FALSE}
Beauty=read.csv("beauty.csv",header=TRUE,sep=",")
#Getting Data from CSV file
```

```{r regression, echo=FALSE, warning=FALSE, include=TRUE, comment=" "}
reg1=lm(lwage~belavg+educ+exper+service+expersq, data=Beauty)
reg2=lm(lwage~belavg+educ+exper+service+expersq+I(belavg*service),data=Beauty)
reg3=lm(lwage~belavg+educ+exper+service+expersq+I(belavg*married),data=Beauty)

stargazer(reg1,reg2,reg3,
se=list(cse(reg1),cse(reg2),cse(reg3)),
title="LOG WAGE VS FACTORS", type="text",df=FALSE,digits=3)
#Descriptive Stats for Q2 
```
### RESPONSES

### What is the estimated plainess penalty on hourly wages? Statisically significant?

If a worker has below average looks, on average their wage will be 15.5% less than someone who has better looks, holding all other factors constant. This effect is statistically significant. 

### What is the estimated plainess penatly for workers in a service industry? How about workers not working in the service industry?

The estimated plainness penalty in the service industry is 17.7%. Meaning that on average with other factors being held constant, someone in the service industry that has below average looks earns 17.7% less than someone with better looks. Someone who has above average looks only faces a plainness penalty of earning 14.7% less who does not work in the service industry. 

### Does the estimated plainess penalty vary with your choice of demographic variable? How?

The estimated plainness penalty decreased by 0.115. Now the plainess penaly is only -12.1% in terms of its effect on wage. Meaning that someone who has below average looks and is also married will on average earn 12.1% less than their counterparts, holding everything else constant.
 






  



 

 


  
  

